---
title: "GSS challange Less Data"
author: "veronica gonzalez"
date: "10/6/22"
output: html_document
---







```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,sex,race,cappun,degree,relig,gunlaw,tvhours,owngun,age,wordsum)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

# Methods

In this variable analysis we will be using graphical,numerical, and inferential results. To find the attitudes towards capitol punishment cappun and independent race. We will also look into the different views from the people. 

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
barchartGC(~race + cappun,data=mydata)
barchartGC(~race + cappun,data=mydata, type="percent")

```

This plot shows that there are 410 white people who are in favor of capitol punishment, and about another 200 of white people who are opposed of the capitol punishment. Around 80 of black people approve of capitol punishment, and 90 of African Americans oppose of this. The other races there are around 50 in favor and 30 opposed of this. Looking at the plot there are way more white people who are in favor of this compare to the african americans and other races. The whites is the majority of the votes who are for this. 

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->



## Now with LESS data (more variables give less data due to NA's) create the approate graphic displays to answer the question.





### Numerical Descriptive Results
```{r}
table1 <- xtabs(~race + cappun, mydata)
rowPerc(table1)
colPerc(table1)
```

The white people are 67% in favor of capitol punishment, but there are also 32% of other white people that are against this. African Americans are 47% for it, and there are 53% opposed of it. For the other races there is a 61% for it and a 39% against this. The whites and the blacks have the biggest split. 

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->






## Inferential Results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```





From the looks of it each group had a completely different opinion according to the fisher test. There is obviously no agreement on capitol punishment. The odd ratio is 2.34326 and we get a 95 % confidence interval. And the p value is just 1.741x10^-5. 

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

`



# Discussion and Conclusion

In this branch we have less data and and more variable. looking at the information we can see that there was a big split between the African Americans and whites. The majority were whites in favor there was no common ground at all. 


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
