---
title: "GSS challange Mydata"
author: "veronica gonzalez"
date: "10/4/22"
output: html_document
---







```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction
```{r eval=FALSE}
mydata <- mydata %>%
mutate(across(where(is.character), as.factor))
```


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

# Methods
The two major variables that are used in this kind of problem are race and capitol punishment. This is why we will be using the file cat_cat.rmd file. Race consists of three factors and captiol punishment has two factors. 
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results


### Graphical Descriptive Results
```{r}
barchartGC(~race + cappun,data=mydata)
barchartGC(~race + cappun,data=mydata, type="percent")

```
This plot states that capitol punishment is dependent on race. There are about twice as many Caucasians that are for Capitol punishment. Now there are about 1/3 of African Americans are completely against Capitol punishment. Now for all the other races the plot states that 1/5 more of people in this category approve of the capitol punishment. 



<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->



## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results
```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The numerical results show that 65% of Caucasians are in favor of capitol punishment. Also, that 58% of African Americans are against the capitol punishment. For the other races 55% are also in favor of the capitol punishment. From the looks of it Caucasian and the other races are for the capitol punishment. The other races and Caucasians are in favor of this and the African Americans are more against this idea. 

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->




## Now with More data



## Inferential Results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The p value is zero indicating that there is a statistical difference towards peoples opinions on capitol punishment and the race.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

````{r}
fisherXY(mydata$race,mydata$cappun)
```

## More data version
The fisher XY states that there is a statistical difference on the position of capitol punishment from Caucasians and African Americans. When we saw the data the P indicated that every race stated that there was a statistical difference in each race. Now, the biggest difference was with the African Americans and Caucasians because they had the lowest P value. 

# Discussion and Conclusion
Looking over all the information the Caucasians were for the capitol punishment. But the African american were against the capitol punishment. There's a huge  difference on the topic and on the race statistically because the p value was zero. There was a 65 percent of Caucasians in favor and a 58 percent of African Americans who were opposed of the idea. But there was a 55 percent of the other races that were for the capitol punishment.  


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
